2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Boxplots and keepers

##### Batters
```{r echo=FALSE}
batters <- players_master %>%
  filter(type == "batter") %>%
  select(type, Name, Team, ADP, 
         PA, R, H, HR, RBI, SB, BB, SO, OBP, OPS)

batters %>%
  select(-type) %>%
  head()  %>%
  kable()
```

##### Pitchers
```{r echo=FALSE}
pitchers <- players_master %>%
  filter(type == "pitcher") %>%
  select(type, Name, Team, ADP,
         IP, SV, SO, HLD, ERA, WHIP)

pitchers %>%
  select(-type) %>%
  head()  %>%
  kable()
```

@@

>>>>

##### Batters
```{r echo=FALSE}
batters <- players_master %>%
  filter(type == "batter") %>%
  select(Name, Team, ADP, type, display_position, positions,
         PA, R, H, HR, RBI, SB, BB, SO, OBP, OPS,)

batters %>%
  select(-(type:positions)) %>%
  head()  %>%
  kable()
```

##### Pitchers
```{r echo=FALSE}
pitchers <- players_master %>%
  filter(type == "pitcher") %>%
  select(Name, Team, ADP, type, display_position, positions,
         IP, SV, SO, HLD, ERA, WHIP)

pitchers %>%
  select(-(type:positions)) %>%
  head()  %>%
  kable()
```

@@

```{r include=FALSE}

z_sums %>%
  filter(type == "batter") %>%
  select(Name, z_rank) %>%
  full_join(batters, by = "Name") %>% 
  mutate(C = grepl("C", display_position)) %>%
  mutate(`1B` = grepl("1B", positions)) %>%
  mutate(`2B` = grepl("2B", positions)) %>%
  mutate(SS = grepl("SS", positions)) %>%
  mutate(`3B` = grepl("3B", positions)) %>%
  mutate(LF = grepl("LF", positions)) %>% 
  mutate(CF = grepl("CF", positions)) %>% 
  mutate(RF = grepl("RF", positions)) -> batters_ranked

z_sums %>%
  filter(type == "pitcher") %>%
  select(Name, z_rank) %>%
  full_join(pitchers, by = "Name") %>%
  mutate(SP = grepl("SP", positions)) %>%
  mutate(RP = grepl("RP", positions)) -> pitchers_ranked

C <- batters_ranked %>%
  filter(C) %>%
  mutate(position = "C")

`1B` <- batters_ranked %>%
  filter(`1B`) %>%
  mutate(position = "1B")

`2B` <- batters_ranked %>%
  filter(`2B`) %>%
  mutate(position = "2B")

`3B` <- batters_ranked %>%
  filter(`3B`) %>%
  mutate(position = "3B")

SS <- batters_ranked %>%
  filter(SS) %>%
  mutate(position = "SS")

LF <- batters_ranked %>%
  filter(LF) %>%
  mutate(position = "LF")

CF <- batters_ranked %>%
  filter(LF) %>%
  mutate(position = "CF")

RF <- batters_ranked %>%
  filter(RF) %>%
  mutate(position = "RF")

SP <- pitchers_ranked %>% 
  filter(SP) %>% 
  mutate(position = "SP")

RP <- pitchers_ranked %>% 
  filter(RP) %>% 
  mutate(position = "RP")

pitcher_positions_ranked <- SP %>%
  bind_rows(RP) %>%
  select(Name, ADP, z_sum, position) %>%
  unique()

positions_ranked <- C %>%
  bind_rows(`1B`) %>%
	bind_rows(`2B`) %>%
	bind_rows(`3B`) %>%
	bind_rows(SS) %>%
  bind_rows(LF) %>% 
  bind_rows(CF) %>% 
  bind_rows(RF) %>% 
  select(Name, ADP, z_sum, position) %>% 
  unique() %>%
  bind_rows(pitcher_positions_ranked) %>%
  arrange(z_sum %>% desc) %>%
  mutate(round = ceiling(ADP/12),
         z_rank = row_number(),
         position = fct_relevel(position, "C","1B", "2B","3B","SS","LF","CF","RF","SP","RP"))

positions_ranked %>%
  filter(ADP <= 300,
         !position %in% c("SP","RP")) %>%
  ggplot(aes(x=position, y=z_sum)) +
  geom_boxplot() +
  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
  labs(x="Position",
       y="Z_Points",
       title="Batter value by position, top 300 drafted") -> pt

ggplotly(pt)
```

This highlights how poor the catcher position is. The upper outliers at the position are roughly equivlanet to the median value of most other positions. If I don't get one of the top four catchers, I'll need to at least make up the 4 z_points somewhere else. That said, the projections indicate that I would do nearly as well with Yasmani Grandal or Buster Posey (rounds 13 and 10, respectively) as I would with the higher in demand J.T. Realmuto and Gary Sanchez (rounds 4 and 5 respectively).

# Draft Prep
Armed with this information, here's what I need before the draft:
1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
2. Add pitchers to the above plot so that I can...
3. ...put together a basic plan of attack for the draft
4. Generate a cheat sheet document to use for the draft

```{r echo=FALSE}

keepers <- c(
  "Justin turner",
  "Miles Mikolas",
  "Whit Merrifield",
  "Archie Bradley",
  "Patrick Corbin",
  "Matt Carpenter",
  "Blake Treinen",
  "Ronald Acuna Jr.",
  "Blake Snell",
  "Lorenzo Cain",
  "Trevor Story",
  "Andrew Benintendi",
  "Mike Clevinger"
)

positions_ranked %>%
  mutate(keeper = (Name %in% keepers)) -> positions_ranked_with_keepers

positions_ranked_with_keepers %>%
  filter(ADP <= 300,
         !keeper) %>%
  ggplot(aes(x=position, y=z_sum)) +
  geom_boxplot() +
  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
  labs(x="Position",
       y="Z_Points",
       title="Player value by position, top 300 drafted") -> ptk

ggplotly(ptk)
```
